---
title: "hw5"
author: "Asahi (Ash) Kuroki"
date: "12/1/2021"
output:
  word_document: default
  html_document: default
  pdf_document: default
---

```{r setup}
knitr::opts_chunk$set(cache = TRUE)
set.seed(123)
```

```{r}
# import packages
library(GGally)
library(caret)
library(rpart.plot)
library(gridExtra)
library(labelVector)
library(tidyverse)
```

Analysis  
  
Processing and Visualizing data  
a) Load the data. Get a summary of the data, report it. Use ggplot to plot a histogram for the distribution of the number of bike-rides.
```{r}
df <- read.csv("bike_day.csv")
summary(df)
```
```{r}
ggplot(data = df, aes(cnt_bike)) + 
  xlim(0, 9000) + 
  ylim(0, 70) + 
  geom_histogram(colour = "grey", fill = "black") + 
  ggtitle("Distrubution of the number of bike-rides") + 
  labs(x = "Number of bikes")
  
```
  
b) Use the function pairs() to produce a plot of the relationships among count, atemp and hum.  
```{r}
pairs(df[,1:3], col = "darkgreen")
```
Comment on distribution

c) (0.2) Split the data into 80% training and 20% testing.  
```{r}
trainRows <- createDataPartition(y = df$cnt_bike, p = 0.8, list = FALSE)
train_set <- df[trainRows,]
test_set <- df[-trainRows,]
```

Train a K-NN model  
a) Decide whether you need to standardize the data or not  
Yes. We need to standardize the data in K-NN. We will standardize all the attributes besides cnt_bike  
```{r}
train_set_stand <- train_set
test_set_stand <- test_set
library(standardize)
#Apply the standardization
train_set_stand[,2:7] <- apply(train_set_stand[,2:7], MARGIN = 2, FUN = scale)
test_set_stand[,2:7] <- apply(test_set_stand[,2:7], MARGIN = 2, FUN = scale)
```
  
b) Train a k-NN model on the appropriate attributes.
```{r}
knn_model <- train(cnt_bike~., train_set_stand, method = "knn")
knn_model 
```






















